\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-04-21 sections/results.tex
Add: Section for DC step supplementary

  % TODO: Supplementary work - Figure S3
  In order to verify this claim, for each of these methods we use the \ac{gg} taxonomy database to assign taxonomies to the representative sequences.
  We then correlate the abundances of matching taxonomies between every pairwise combination of DC methods (Figure \ref{fig:figureS1}A and B).
  The \ac{esv} tables generated by methods that perform denoising are very similar to each other ($\sim0.91$) and the \ac{otu} tables generated by the clustering methods are very similar to each other ($\sim0.9$), but results of denoising and clustering are highly uncorrelated with each other ($\sim0.4$) (Figure \ref{fig:figureS1}C).

>>>>

  % TODO: Supplementary work - Figure S3
  In order to verify this claim, for each of these methods we use only the top 100 reference sequences and recalculate the distance metrics (Figure \ref{fig:figureS3}).
  We observe that the both the weighted and unweighted UniFrac distances are decreased considerably implying that the top reference sequences generated by the different methods are similar to each other.

### 2022-04-21 sections/supplementary.tex
Add: Script to generate Figure S3
Add: Section for DC step supplementary

>>>>

    % TODO: Write something about TSNE
    \begin{figure}[H]
      \centering
      \includegraphics[width=1.0\linewidth]{figure_s2.pdf}
    \end{figure}
    \begin{figure}[H]
      \centering
        \caption{
          \textbf{The TSNE plot of the networks inferred by various methods}.
        }
      \label{fig:figure_s2}
    \end{figure}
    \FloatBarrier
    \newpage

  \subsection*{Effects of low abundant reference sequences in the \ac{dc} step}

    Figure~\ref{fig:figureS3} is similar to Figure~\ref{fig:figure3} shows the average UniFrac distance between reference sequences generated by the various methods in the \ac{dc} step.
    In Figure~\ref{fig:figureS3} however, we use only the top  100 reference sequences (by abundance) for this calculation.
    We observe that both the weighted and unweighted UniFrac distances are reduced compared to the figure with the all the reference sequences.
    This shows that the most abundant reference sequences generated by the methods are similar to each other.

    \begin{figure}[H]
      \centering
      \includegraphics[width=1.0\linewidth]{figure_s3.pdf}
    \end{figure}
    \begin{figure}[H]
      \centering
        \caption{
          \textbf{The UniFrac distance between the 100 most abundant reference sequences generated by various method in the \ac{dc} step}
        }
      \label{fig:figure_s3}
    \end{figure}
    \FloatBarrier
    \newpage
